---
title: '<font color = "#FF6F00  " size = "8px">Statistical Computing and Simulation</font> <br><font color = "#F1C40F" size = "6px"> Homework 01</font>'
author: "Charles and Kevin"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: true
---
```{r message=FALSE}
library(dplyr)
library(kableExtra)
library(knitr)
library(nortest)
library(gridExtra)
library(grid)
library(pracma)
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html")
```

不使用科學記號
```{r warning=FALSE}
options(scipen=999)
```

# Question 01 
## (a) The mid-Square Method
Write a computer program using the Mid-Square Method using 6 digits to
generate 10,000 random numbers ranging over [0, 999999]. Use the Kolmogorov-Smirnov Goodness-of-fit test to see if the random numbers that you create are uniformly distributed. (Note: You must notify the initial seed number used, and you may adapt 0.05 as the α value. Also, you may find warning messages for conducting the Goodness-of-fit test, and comment on the Goodness-of-fit test. )
```{r}
# N 為模擬次數, x 為起始值(亂數決定)#
set.seed(2)
x <- floor(runif(1)*10^6)
N <- 10000
u <-  matrix(0,N/5,5)
for(i in 1:N/5){
  for( j in 1:5){
    y <-  x^2 %>% as.vector()
    while(nchar(y) != 12){
      y <- paste0(0,y)}
    x <- substr(y,4,9) %>% as.numeric()
    u[i,j]  <- substr(y,4,9)}}
kable(u) %>% kable_styling() %>% scroll_box(height = "200px")
hist(as.numeric(u)/1000000, main = " The mid-square method ",xlab= "Data",breaks = 400)
P <- ks.test(as.numeric(u)/1000000,'punif')
P$p.value
print(ifelse(P$p.value <= 0.05,"Reject H0; This is not an uniform distribution","Do not reject H0; This is an uniform distribution"))
# P value < alpha = 0.05, reject H0: This is uniform distribution #
```
## (b) The combination of 3 multiplicative congruential generators
Consider the combination of 3 multiplicative congruential generators, i.e.,
<center><font size = 3>$u_i=\frac{x_i}{30269}+\frac{y_i}{30307}+\frac{z_i}{30323}$(mod 1)</font></center>
with $x_i$ =171$x_{i-1}$ (mod30269), $y_i$ =172 $y_{i-1}$ (mod30307), $z_i$ =170$z_{i-1}$ (mod30323). Use both the $x^2$ and Kolmogorov-Smirnov Goodness-of-fit tests to check if the
data are from U(0,1) distribution.
```{r }
# N 為模擬次數, (x, y, z) 為任意給定值 #
N = 10000
x <- 5; y <- 8; z <- 34
u <- NULL
for(i in 1:N){
  x <- (x * 171 ) %% 30269
  y <- (y * 172 ) %% 30307
  z <- (z * 170 ) %% 30323
  temp <- (x/30269 + y/30307 + z/30323) %% 1
  u <- c(u, temp)}
u <- matrix(u,ncol=5)
kable(u) %>% kable_styling() %>% scroll_box(height = "200px")
h = hist(u,main='The combination of 3 multiplicative congruential generators',xlab = 'Data')
# Kolmogorov-Smirnov #
p1 <- ks.test(u,'punif')
p1$p.value
print(ifelse(p1$p.value <= 0.05,"Reject H0; This is not an uniform distribution","Do not reject H0; This is an uniform distribution"))
# Chisq test #
p2 <- chisq.test(h$counts,p = rep(1/length(h$counts),length(h$counts)))
p2$p.value
print(ifelse(p2$p.value <= 0.05,"Reject H0; This is not an uniform distribution","Do not reject H0; This is an uniform distribution"))
```

## (c) $U_{n+1} = ($π$ +$U_n)^5$(mod 1)
The calculators use$U_{n+1}$ = ($π$ +$U_n)^5$(mod 1) to generate random numbers
between 0 and 1. Compare the result with those in (a) & (b), and discuss your finding based on the comparison.
```{r warning=FALSE}
# N 為模擬次數 #
set.seed(5)
u0 <- runif(1,0,1)
N <- 10000
U <- NULL
for(i in 1:N){
  if(i == 1){U[i] <- ((pi+u0)^5) %% 1}
  else{
  U[i] <- ((pi+U[i-1])^5) %% 1}}
U <- matrix(U,ncol=5)
kable(U) %>% kable_styling() %>% scroll_box(height = "200px")
h <- hist(U,main = 'Simulation',xlab = 'Data')
p1 <- ks.test(U,'punif')
p1$p.value
print(ifelse(p1$p.value <= 0.05,"Reject H0; This is not an uniform distribution","Do not reject H0; This is an uniform distribution"))
p2 <- chisq.test(h$counts,p = rep(1/length(h$counts),length(h$counts)))
p2$p.value
print(ifelse(round(p2$p.value, digits = 3)<= 0.05,"Reject H0; This is not an uniform distribution","Do not reject H0; This is an uniform distribution"))
```
## Result and Discuss

# Question 02
There are several ways for checking the goodness-of-fit for empirical data. In specific, there are a lot of normality tests available in R. Generate a random sample of size 10, 50, and 100 from N(0,1) and t-distribution (with degrees 10 and 20) in R. You may treat testing random numbers from t-distribution as the power. For a level of significance α = 0.05 test, choose at least four normality tests in R (“nortest” module) to check if this sample is from N(0,1). Tests used can include the Kolmogorov-Smirnov test and the Cramer-von Mises test. Note that you need to compare the differences among the tests you choose.

## 使用的常態檢定 6種

-Kolmogorov-Smirnov test -Anderson-Darling test -Shapiro-Francia test

-Cramer-von Mises test -Lilliefors test -Pearson Chi-Square test
```{r warning=F}
pvalue <- function(t1){
  kp <- ks.test(t1,'pnorm')
  ap <- ad.test(t1)
  sp <- sf.test(t1)
  cp <- cvm.test(t1)
  lp <- lillie.test(t1)
  pp <- pearson.test(t1)
  AA <- matrix(c(kp$p.value,ap$p.value,sp$p.value,cp$p.value,lp$p.value,pp$p.valuw),6,1)
  return(AA)
}
```

## t distribution with df=10
```{r warning=FALSE}
# 抽取樣本數，實驗模擬1000次，計算各檢定的型二誤差機率 #
set.seed(5)
sample <- c(10,50,100)
PPP <- NULL
for(j in 1:3){
  PPP1 <- NULL
  for(i in 1:1000){
    t1 <- rt(sample[j],10)
    PPP1 <- cbind(PPP1,pvalue(t1))}
  PPP <- rbind(PPP,PPP1)}

PoWeR_10 <- apply(PPP<0.05,1,sum) /1000
PoWeR_10 <- matrix(PoWeR_10,3,6,byrow = T)
colnames(PoWeR_10) <- c("KS.test","AD.test","SF.test","CVM.test","Lillie.test","Pearson.test")
rownames(PoWeR_10) <- c("n = 10","n = 50","n = 100")
# 繪圖表格 #
# 1000次模擬實驗，計算Type 2 error的次數，成功拒絕H0的次數(P value < 0.05 ) #
kable(PoWeR_10, "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  add_header_above(c(" Number of sample" = 1, "t distribution with df=10"=6))
```

## t distribution with df=20
```{r warning=FALSE}
# 抽取樣本數，實驗模擬1000次，計算各檢定的型二誤差機率 #
sample <- c(10,50,100)
PPP <- NULL
for(j in 1:3){
  PPP1 <- NULL
  for(i in 1:1000){
    t1 <- rt(sample[j],20)
    PPP1 <- cbind(PPP1,pvalue(t1))}
  PPP <- rbind(PPP,PPP1)}

PoWeR_20 <- apply(PPP<0.05,1,sum)/1000
PoWeR_20 <- matrix(PoWeR_20,3,6,byrow = T)
colnames(PoWeR_20) <- c("KS.test","AD.test","SF.test","CVM.test","Lillie.test","Pearson.test")
rownames(PoWeR_20) <- c("n = 10","n = 50","n = 100")
# 繪圖表格 #
# 1000次模擬實驗，計算在不同樣本下，各個test的的次數，成功拒絕H0的次數(P value < 0.05 ) #
kable(PoWeR_20, "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  add_header_above(c(" Number of sample" = 1, "t distribution with df=20"=6))
```

## Normal(0,1) 
```{r warning=FALSE}
# 抽取樣本數，實驗模擬1000次，計算各檢定的型二誤差機率 #
sample <- c(10,50,100)
PPP <- NULL
for(j in 1:3){
  PPP1 <- NULL
  for(i in 1:1000){
    t1 <- rnorm(sample[j],0,1)
    PPP1 <- cbind(PPP1,pvalue(t1))}
  PPP <- rbind(PPP,PPP1)}

PoWeR_30 <- apply(PPP<0.05,1,sum)/1000
PoWeR_30 <- matrix(PoWeR_30,3,6,byrow = T)
colnames(PoWeR_30) <- c("KS.test","AD.test","SF.test","CVM.test","Lillie.test","Pearson.test")
rownames(PoWeR_30) <- c("n = 10","n = 50","n = 100")
# 繪圖表格 #
# 1000次模擬實驗，計算Type 2 error的次數，成功拒絕H0的次數(P value < 0.05 ) #
kable(PoWeR_30, "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  add_header_above(c(" Number of sample" = 1, "Normal (0,1)"=6))
```

# Question 03
Write your own R programs to perform Gap test, Permutation test, and run test. Then use this program to test if the uniform random numbers generated from Minitab (or SAS, SPSS, Excel) and R are independent.

<center>H0: This is an independent data.</center>
<center>H1: This is not an independent data.</center>

## 從Ｒ及Excel的Uniform (0,1)生成10000萬筆隨機資料
```{r}
# R
set.seed(4)
x <- runif(10000,0,1)
s <- matrix(x,ncol = 5)
kable(s) %>% kable_styling() %>% scroll_box(height = "200px")
hist(x,breaks =10,main = 'Data from R',xlab = "Data")
# Excel 
y <- read.csv('/Users/kevinpiger/Desktop/碩一下/統模/Homework01/excelrandom.csv') %>% as.vector()
y <- y$x %>% as.vector()
s <- matrix(y,ncol=5)
kable(s) %>% kable_styling() %>% scroll_box(height = "200px")
hist(y,breaks = 10,main = 'Data from EXCEL',xlab = "Data")
```

## Run test
function: run(w,c),w為資料，須介於0,1之間，c為顯著水準；以0.5作為分界點，大於0.5定義為S成功，小於等於0.5定義為F失敗，$n_1$為S的數量，$n_2$為F的數量，Runs為總Run的個數，當$n_1$ > 10且 $n_2$>10時，Runs為近似常態分配N($\frac{2n_1n_2}{n_1+n_2}+1$,$\frac{2n_1n_2 (2n_1n_2-n_1-n_2)}{((n_1+n_2 )^2 (n_1+n_2-1)}$)
Rejection region:{ $|Z_0| ≥ |Z_{α/2}|$ }，$Z_0$為Runs標準化的檢定統計量，α=0.05。($n_2$以總個數length(rx)減去n1的個數表示)
function: run(w,c); w為欲檢定資料, c為顯著水準。
```{r}
run =  function(w,c){
  rx <- w
  rx[rx > 0.5] = "S"
  rx[rx <= 0.5] = "F"
  # 總ＲＵＮ數 #
  RUNS <- sum(rx[-1] != rx[-(length(rx))]) + 1
  # test #
  n1 <- sum(rx == "S")
  muR <- (2 * n1 *(length(rx)- n1))/ length(rx) + 1
  sigma_R <- 2 * n1 *(length(rx)- n1) *( 2*n1*(length(rx) - n1) - length(rx))/(length(rx)^2 * (length(rx) -1))
  z2 <-( RUNS - muR ) / sqrt(sigma_R)
  return(print(ifelse(abs(z2) >= qnorm(1-c/2,0,1), paste("Z = ",round(abs(z2),digits = 3),' >= ',qnorm(1-c/2,0,1),"Reject Ho "),paste("Z= ",round(abs(z2),digits = 3),' < ',qnorm(1-c/2,0,1),"Do not reject Ho "))))}
# 第一個位置請放資料(vector),第二個位置放顯著水準 #
run(x,0.05)
run(y,0.05)
```

## Gap test
function: gap(w,c,d1,d2); w為欲檢定資料, c為顯著水準, 選取介於 0, 1間的兩個數0< d1 < d2 < 1，alpha為d1值, beta為d2值
考慮介於α與β間的亂數，介於α與β間的亂數為 1其餘為 0，間隔應與幾何分配有關，間隔個數P(K = k) = (β − α)×(1−(β −α ))k , k = 0,1,...
最後在代入卡方檢定
```{r warning= FALSE}
gap <- function(w,c,d1,d2){
sample <- w
alpha <- min(d1); beta <- max(d2)
fgap <- (sample <= beta & alpha <= sample)*1
fgap_p <- which(fgap == 1)
tmp <- fgap_p[-1]-fgap_p[-length(fgap_p)] - 1
tmp1 <- tmp %>% table() %>% as.data.frame();tmp1
names(tmp1) <- c('Gap','Freq')
p <- chisq.test(as.integer(tmp1$Freq), p =  dgeom(as.integer(tmp1$Gap),prob = beta - alpha),rescale.p = T)
return(print(ifelse(p$p.value >= c,paste("p_value",round(p$p.value,digits = 3),' > ',c,"Do not reject H0"),paste("p_value",round(p$p.value,digits = 3),'<=',c, 'Reject H0'))))}

# 第一個位置請放資料(vector),第二個位置放顯著水準 #
gap(x,0.05,0.2,0.8)
gap(y,0.05,0.2,0.8)
```

## Permutation test
function: Permutation.test(w,c); W為欲檢定資料, c為顯著水準。
```{r}
permutation.test <- function(W,c){
  W <- matrix(W , nrow = 4 ,byrow = F )
  W1 <- apply(W , 2 , rank)
  W2 <- W1[1,]*1000+W1[2,]*100+W1[3,]*10+W1[4,];W2
  p <- chisq.test(table(W2))
  return(print(ifelse(p$p.value >= c,paste("p_value",p$p.value,'>',c,"Do not reject H0"),
                      paste("p_value",p$p.value,'<=',c, 'Reject H0'))))
}

permutation.test(x,0.05)
permutation.test(y,0.05)
```

## Conclusion Both data of R and Excel are random.
# Question 04
## (a) 
$\sum\limits_{i=1}^{12}U_i-6$ can be used to approximate N(0,1) distribution, where $U_i$'s are
random sample from U(0,1).
Based on α = 0.05, compare the results of the Chi-square test and the Kolmogorov-Smirnov test, and see if there are any differences.
<center>H0: This is an approximate N(0,1) distribution.</center>
<center>H1: This is not an approximate N(0,1) distribution.</center>
```{r warning=FALSE}
# 抽10000組 x, 每組都是12個U抽自U(0,1),去形成1000個近似常態資料樣本 #
# 再用ks test 以及 chisq test去檢測是否近似常態資料, alpha =0.05 #
N <- 10000
x <- NULL
for(i in 1:N){
  x[i] <- runif(12) %>% sum() - 6}
# 繪製長條圖 #
h <- hist(x,main = "Simulation of x", xlab = 'Data')
# ks test #
p1 <- ks.test(x,"pnorm")
print(ifelse(p1$p.value >= 0.05,paste('p value =',round(p1$p.value,digits = 3),"> 0.05","Do not reject H0."),paste('p value =',round(p1$p.value,digits = 3),"<= 0.05","Reject H0.")))

# Chisq test #
p2 <- chisq.test(h$counts,dnorm(h$counts))
print(ifelse(p2$p.value >= 0.05,paste('p value =',round(p2$p.value,digits = 3),"> 0.05","Do not reject H0."),paste('p value =',round(p2$p.value,digits = 3),"<= 0.05","Reject H0.")))
```
Conclusion: ks.test以及Chisq.test都不拒絕H0。

```{r}
#4-b
#Design two tests of independence (which are not the same as you saw in class) and apply them on the random sample that you generate.
#(1) idea by Lin, YC
y <- rank(x)
plot(1:N,y,ylab = "Rank",xlab = 'Oeder of x')
abline(v = 5000,col = 'red')
abline(h = 5000,col = 'red')
r1 <- length(which(y[1:5000]<5000))
r2 <- length(which(y[1:5000]>=5000))
r3 <- length(which(y[5001:10000]<5000))
r4 <- length(which(y[5001:10000]>=5000))
R <- c(r1,r2,r3,r4)
R0 <-sum((R-2500)^2/2500)
ifelse(R0 >= qchisq(0.95,3),paste('chisq value',R0,'>=', qchisq(0.95,3),'Reject H0'),paste('chisq value',R0,'<', qchisq(0.95,3),"Do not reject H0"))

#(2) rank + run.test
y <- y / 10000
run(y,0.05)
```

# Question 05
Use the bisection, false positions, and secant methods to find the roots, and
check your answers with the functions in R.
You need to specify the starting points, convergence criterion, and number of iterations.

the question of (a) is $f(x)=e-\frac{1}{3.5+x}$

the question of (b) is $f(x)=\frac{e^x}{\sqrt{1+x^2}}-0.5$

the question of (c) is the eigenvalue of matrix A 
$\begin{bmatrix}
2&3&4\\
3&4&5\\
4&5&6 
\end{bmatrix}$</font>

## Method
### Bisection Method
```{r setup = FALSE}
bisection.method<-function(f,a,b){
fa <- f(a) ; fb <- f(b)
c <- (a+b)/2 ; fc <- f(c)
na=c();nb=c();nc=c();nfa=c();nfb=c();nfc=c()
if((fa*fb)>0){
  print("Wrong Input")
}
i <- 0
W1 <- c(a,b,fa,fb,c,fc)
while (abs(b-a) > 0.00001){
  i<-i+1
  fa <- f(a) ; fb <- f(b) ; fc <- f(c)
  if((fa*fc)<0){ 
    a = a ; fa = fa
    b = c ; fb = fc
    na = c(na,a) ; nb = c(nb,b)
    nfa = c(nfa,fa) ; nfb = c(nfb,fb)
  }
  else{ 
    a = c ; fa = fc
    b = b ; fb = fb
    na = c(na,a) ; nb = c(nb,b) ; nfa = c(nfa,fa) ; nfb = c(nfb,fb)
  }
  c = (a+b)/2 ; fc <- f(c)
  nc = c(nc,c) ; nfc = c(nfc,fc)
}
W2 <- c(na,nb,nfa,nfb,nc,nfc)
W2 <- matrix(data = W2,ncol = 6,byrow = F)
W2 <- rbind(W1,W2)
W <- data.frame("a"=W2[,1],"b"=W2[,2],"func.a"=W2[,3],"func.b"=W2[,4],"c"=W2[,5],"func.c"=W2[,6])
b=b
print('covegence criterion : |b-a|<1e-6')
print(paste('number of iterations : ',i))
print(paste('approximation root :', b))
print(knitr::kable(W,"rst",digits = 7))
kable(W,"html") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% add_header_above(c(" Bisection Method" = 6))%>% kable_styling() %>% scroll_box(height = "200px")
}
```
### False Position Method
```{r setup = FALSE}
false.position.method <- function(f,a,b){
fa <- f(a) ; fb <- f(b)
c <- a-(fa*(b-a)/(fb-fa)) ; fc <- f(c)
e=abs(c-b)
na=c();nb=c();nc=c();ni=c();nfa=c();nfb=c();nfc=c()
if((fa*fb)>0){
  print("Wrong Input")
}
i=0
W1<-c(a,b,c,fa,fb,fc)
while(e>0.00001){
  i <- i+1
  fa <- f(a) ; fb <- f(b)
  c <- b-(fb*(b-a)/(fb-fa)) ;  fc <- f(c)
  if(sign(fc) == sign(fa)){
    e <- abs(c-a)
    a <- c ; fa <- fc
    b <- b ; fb <- fb
    na = c(na,a) ; nb = c(nb,b)
    nfa=c(nfa,fa) ; nfb = c(nfb,fb)
  }
  else{
    e <- abs(c-b)
    a <- a ; fa <- fa
    b <- c ; fb <- fc
    na = c(na,a) ; nb = c(nb,b)
    nfa = c(nfa,fa) ; nfb = c(nfb,fb)
  }
  nfc = c(nfc,fc) ; nc = c(nc,c)
}
W2<-c(na,nb,nc,nfa,nfb,nfc)
W2<-matrix(data=c(na,nb,nc,nfa,nfb,nfc),ncol=6,byrow = F)
W<-rbind(W1,W2)
W<-data.frame("a"=W2[,1],"b"=W2[,2],"c"=W2[,3],"func.a"=W2[,4],"func.b"=W2[,5],"func.c"=W2[,6])
b=b
print('covegence criterion : |Cn-Cn-1|<1e-5')
print(paste('number of iterations : ',i))
print(paste('approximation root :', c))
print(knitr::kable(W,"rst",digits = 7))
kable(W,"html") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% add_header_above(c(" False Position Method" = 6))%>% kable_styling() %>% scroll_box(height = "200px")
}
```
### Secant Method
```{r setup = FALSE}
secant.method<-function(f,a,b){
  fa <- f(a) ; fb <- f(b)
  c <- b-((b-a)/(fb-fa))*fb;fc <- f(c)
  d = abs(b-a)
  W1 <- c(a,b,fa,fb,c,fc)
  na=c();nb=c();nc=c();nfa=c();nfb=c();nfc=c()
  i=0
  while(d>0.000001){
    i <- i+1
    fa <- f(a)
    fb <- f(b)
    na = c(na,a) ;  nb = c(nb,b) ; nfa = c(nfa,fa); nfb = c(nfb,fb)
    c <- b-((b-a)/(fb-fa))*fb
    a = b ; b = c
    c2 <- b-((b-a)/(fb-fa))*fb
    nc = c(nc,c2) ; fc <- f(c2) ; nfc = c(nfc,fc)
    d = abs(b-a)
  }
  W2 <- c(na,nb,nc,nfa,nfb,nfc)
  W2 <- matrix(data=c(na,nb,nc,nfa,nfb,nfc),ncol=6,byrow = F)
  W2 <- rbind(W1,W2)
  W <- data.frame("a"=W2[,1],"b"=W2[,2],"c"=W2[,3],"func.a"=W2[,4],"func.b"=W2[,5],"func.c"=W2[,6])
  b = b
  print('covegence criterion : |Cn-Cn-1|<1e-5')
  print(paste('number of iterations : ',i))
  print(paste('approximation root :', b))
  print(knitr::kable(W,"rst",digits = 7))
  kable(W,"html") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% add_header_above(c(" Secant Method" = 6))%>% kable_styling() %>% scroll_box(height = "200px")
}
```
## Solve problem
### (a)
<tr><b>The question of (a)  </b></tr>
<font size="4px"><center>$f(x)=e-\frac{1}{3.5+x}$</center></font>
```{r}
f <- function(x){
  return(exp(1)-(1/(3.5+x)))
}
```
```{r}
curve(f,xlim = c(-5,0))
abline(h=0)
```
<br><center>當$x=-3.5$，其函數值不存在</center></br>
<br><center>當$x<-3.5$，其函數值皆為正</center></br>
<br><center>我們選取?$a=-3.2 ,b=-3$作為起始點</center></br>
#### R_uniroot
```{r}
# We choose start point a=-3.2 b=-3.0
uniroot(f,c(-3.2,-3))
```
#### Bisection Method
```{r}
# We choose start point a=-3.2 b=-3.0
bisection.method(f,-3.2,-3)
```
#### False Position Method
```{r}
# We choose start point a=-3.2 b=-3.0
false.position.method(f,-3.2,-3)
```
#### Secant Method
```{r}
# We choose start point a=-3.2 b=-3.0
secant.method(f,-3.2,-3)
```
Conclusion 

### (b)
<tr><b>The question of (b)</b></tr>
<font size="4px"><center> ${f(x)=\frac{e^x}{\sqrt{1+x^2}}-0.5}$ </center></font>
```{r}
f<-function(x){
  return((exp(-x))/sqrt(1+x^2)-0.5)
}
```
```{r}
curve(f,xlim = c(-0,1))
abline(h=0)
```
<br><center>由圖形觀察出其根介於(0,1)之間/center></br>
<br><center>我們選取?$a=0 ,b=1$作為起始點</center></br>

#### R_uniroot
```{r}
# We choose start point a=0 b=1
uniroot(f,c(0,1))
```
#### Bisection Method
```{r}
# We choose start point a=0 b=1
bisection.method(f,0,1)
```
#### False Position Method
```{r}
# We choose start point a=0 b=1
false.position.method(f,0,1)
```
#### Secant Method
```{r}
# We choose start point a=0 b=1
secant.method(f,0,1)
```
Conclusion 

### (c)
<tr><b>The question of (c)  </b></tr>
<font size="4px"><center>the eigenvalue of A=$\begin{bmatrix}
2&3&4\\
3&4&5\\
4&5&6 
\end{bmatrix}$</center></font>
```{r}
A<-c(2,3,4,3,4,5,4,5,6)
A<-matrix(A,ncol=3,byrow=T)
eigen(A)
f <- function(x){
  return((2-x)*(4-x)*(6-x)+3*5*4+4*3*5-(2-x)*5*5-4*(4-x)*4-3*3*(6-x))
}
f(0)
```
```{r}
curve(f,xlim = c(-5,15))
abline(h=0)
```
<br><center>因為函數為三次式，我們將圖形更進一步分割</center></br>
```{r}
curve(f,xlim = c(-1,1))
abline(h=0)
```

```{r}
curve(f,xlim = c(12,13))
abline(h=0)
```
<br><center>我們選取三組起始點來計算三根?</center></br>
<br><center>$a=-1 ,b=-0.2$作為第一組</center></br>
<br><center>$a=-0.2,b=1$作為第二組</center></br>
<br><center>$a=12 ,b=13$作為第三組</center></br>

#### R_uniroot
```{r}
#第一組
# We choose start point a=-1 b=-0.2
uniroot(f,c(-1,-0.2))
```
```{r}
#第二組
# We choose start point a=-0.2 b=1
uniroot(f,c(-0.2,1))
```
```{r}
#第三組
# We choose start point a=12 b=13
uniroot(f,c(12,13))
```
#### Bisection Method
##### 第一組(-1,-0.2)
```{r}
bisection.method(f,-1,-0.2)
```
##### 第二組(-0.2,0)
```{r}
bisection.method(f,-0.2,1)
```
##### 第三組(12,13)
```{r}
bisection.method(f,12,13)
```
#### False Position Method 
##### 第一組(-1,-0.2)
```{r}
# We choose start point a=-1 b=-0.2
false.position.method(f,-1,-0.2)
```
##### 第二組(-0.2,1)
```{r}
# We choose start point a=-0.2 b=-1
false.position.method(f,-0.2,-1)
```
##### 第三組(12,13)
```{r}
# We choose start point a=12 b=12
false.position.method(f,12,13)
```
#### Secant Method
##### 第一組(-1,-0.2)
```{r}
# We choose start point a=-1 b=-0.2
secant.method(f,-1,-0.2)
```
##### 第二組(-0.2,0)
```{r}
# We choose start point a=-0.2 b=1
secant.method(f,-0.2,1)
```
##### 第三組(12,13)
```{r}
# We choose start point a=12 b=13
secant.method(f,12,13)
```
Conclusion 

# Question 06
Consider a multinomial observation X =($x_1,x_2,x_3,x_4$)with class probabilities given by ($p_1,p_2,p_3,p_4$)=($\frac{2+θ}{4}$,$\frac{1-θ}{4}$,$\frac{1-θ}{4}$,$\frac{θ}{4}$), where 0<$\theta$ <1. The sample
size is n= $\sum{x_i}$ and the parameter $\theta$ is to be estimated from the observedfrequencies (1997, 906, 904, 32), i.e., sample size 3839. Use the secant, Ridder’s (or Brent’s), and Newton-Raphosn methods to find the MLE (via l'($\theta$)). Youmay choose your own starting points and convergence criterion (preferred $10^{-6}$ or smaller)

## Define f.o.c likelihood function
```{r}
f = function(x){(1997/(2+x)-1810/(1-x)+32/x)/4}
```

```{r}
curve(f,xlim = c(0,0.1))
abline(h=0, col = "red")
```

## Newton-Raphosn Method
```{r warning = FALSE}
#Newton
Newton <- function(f,S,tol){
i=1
N_table <- matrix(c(0,S,f(S)),1,3)
colnames(N_table) <- c('Iterative','x','f(x)')
tr = tol
while(tr>=tol){
  ss <- N_table[i,2] - f(N_table[i,2])/grad(f,N_table[i,2])
  tr <- abs(ss-N_table[i,2])
  i = i+1
  N_table <- rbind(N_table,c(i-1,ss,f(ss)))
}
  print("Newton's Method ")
  print('covegence criterion : tolerence <1e-6')
  print(paste('number of iterations : ',i))
  print(paste('approximation root :', ss))
  print(knitr::kable(N_table,"rst",digits = 7))
  kable(N_table, "html") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% add_header_above(c("Newton-Raphosn Method"= 3 ))
}
```
## Ridder method by our hand
```{r}
#Ridders method function
ridders.method<-function(f,a,b){
  fa <- f(a) ; fb <- f(b) ; 
  c <- (a+b)/2 ; fc <- f(c)
  e_Q <- (fc+sign(fb)*(fc^2-fa*fb)^(1/2)/fb)
  d <- c-(c-a)*sign(fa-fb)*(fc/(fc^2-fa*fb)^(1/2))
  fd <- f(d)
  na=c();nb=c();nd=c();nfa=c();nfb=c();nfd=c()
  if((fa*fb)>0){
    print("Wrong Input")
  }
  i <- 0
  W1 <- c(a,b,fa,fb,d,fd)
  while (abs(b-a) > 0.000001){
    i<-i+1
    fa <- f(a) ; fb <- f(b) ; fd <- f(d)
    
    if((fa*fd)<0){ 
      a = a ; fa = fa
      b = d ; fb = fd
      na = c(na,a) ; nb = c(nb,b)
      nfa = c(nfa,fa) ; nfb = c(nfb,fb)
    }
    else{ 
      a = d ; fa = fd
      b = b ; fb = fb
      na = c(na,a) ; nb = c(nb,b) ; nfa = c(nfa,fa) ; nfb = c(nfb,fb)
    }
    c = (a+b)/2 ; fc <- f(c)
    d <- c-(c-a)*sign(fa-fb)*(fc/(fc^2-fa*fb)^(1/2)) ; fd <- f(d)
    nd = c(nd,d) ; nfd = c(nfd,fd)
  }
  W2 <- c(na,nb,nfa,nfb,nd,nfd)
  W2 <- matrix(data = W2,ncol = 6,byrow = F)
  W2 <- rbind(W1,W2)
  W <- data.frame("a"=W2[,1],"b"=W2[,2],"func.a"=W2[,3],"func.b"=W2[,4],"d"=W2[,5],"func.d"=W2[,6])
  d=b
  print("Ridder's Method ")
  print('covegence criterion : |b-a|<1e-6')
  print(paste('number of iterations : ',i))
  print(paste('approximation root :', d))
  print(knitr::kable(W,"rst",digits = 7))
  kable(W,"html") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% add_header_above(c(" Ridder Method" = 6))
}
ridders.method(f,0.02,0.05)
```
## Uniroot by R
```{r}
# uniroot
uniroot(f,c(0.02,0.05),tol = 10^(-6))
```
## Newton
```{r}
Newton(f,0.05, tol = 0.000001)
```


## Ridder method by R
```{r}
# ridder
ridders(f,0.02,0.05)
```
## Secant.method
```{r}
# Secant
secant.method(f,0.02,0.05)
```

## Bisection
```{r}
# Bisection
bisection.method(f,0.02,0.05)
```

## false position 
```{r}
# false position 
false.position.method(f,0.02,0.05)
```

## 判斷是否為極大值
```{r}
# s.o.c
grad(f,0.0357123) < 0

```

<center><font color="red" size="10px"><b>Do you ever shine?</b></font></center>
